An example of extremely reproducible enrichment analysis

### 2023-03-24 example.Rmd
fig size

---
title: "An example of extremely reproducible enrichment analysis"
author: "Mark Ziemann & Anusuiya Bora"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 7
    fig_height: 7
theme: cosmo
---

@@

```{r,venn1,fig.width=6,fig.height=6}

@@

# reads per million normalisation
rpm <- apply(mxf,2, function(x) { x/sum(x) * 1000000} )
colnames(rpm) <- c("UNTR1","UNTR2","UNTR3","TRT1","TRT2","TRT3")
gnames_up <- gsets[[which(names(gsets) == upname)]]
gnames_dn <- gsets[[which(names(gsets) == dnname)]]
gene_ids <- rownames(mxf)
gene_names <- sapply(strsplit(gene_ids," "),"[[",2)
rpm_up <- rpm[which(gene_names %in% gnames_up),]
rpm_dn <- rpm[which(gene_names %in% gnames_dn),]
colsidecols <- c("blue","blue","blue","red","red","red")
heatmap.2(rpm_up,scale="row",trace="none",margins=c(10,10),main=upname,ColSideColors=colsidecols)
heatmap.2(rpm_dn,scale="row",trace="none",margins=c(10,10),main=dnname,ColSideColors=colsidecols)

>>>>

---
title: "An example of extremely reproducible enrichment analysis"
author: "Mark Ziemann & Anusuiya Bora"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 5
    fig_height: 5
theme: cosmo
---

@@

```{r,venn1}

@@

# reads per million normalisation
rpm <- apply(mxf,2, function(x) { x/sum(x) * 1000000} )
colnames(rpm) <- c("UNTR1","UNTR2","UNTR3","TRT1","TRT2","TRT3")
gnames_up <- gsets[[which(names(gsets) == upname)]]
gnames_dn <- gsets[[which(names(gsets) == dnname)]]
gene_ids <- rownames(mxf)
gene_names <- sapply(strsplit(gene_ids," "),"[[",2)
rpm_up <- rpm[which(gene_names %in% gnames_up),]
rpm_dn <- rpm[which(gene_names %in% gnames_dn),]
colsidecols <- c("blue","blue","blue","red","red","red")
heatmap.2(rpm_up,scale="row",trace="none",margins=c(10,15),main=upname,ColSideColors=colsidecols)
heatmap.2(rpm_dn,scale="row",trace="none",margins=c(10,15),main=dnname,ColSideColors=colsidecols)
